Preregistration

### 2021-04-12 preregistration.Rmd
fix seed

setup <- expand_grid(n_obs = n_obs,
                     truth = model_truth,
                     same = model_same,
                     differ = model_differ,
                     mod_load = c(3),
                     mod_int = c(3),
                     extract_fns = list(extract_fns),
                     group.equal = list(c("loadings", "intercepts")),
                     auto.fix.first = FALSE)
to_export <- ls_funs() %>% map(get)
to_export <- c(list(setup = setup), to_export)
RNGkind("L'Ecuyer-CMRG")
set.seed(params$seed)
res_raw %<-% 
  generate_data(n_sim,
                setup,
                furrr_options(
                  globals = to_export,
                  seed = TRUE,
                  packages = c("furrr", "lavaan", "tidyverse")
                ))
```

@@

```{r checksum}
# compute checksum using md5
checksum <- digest::digest(res_raw, "md5")
if(checksum != "856fed767a7e0c3efcb5ac76359f7707"){
  warning("Mismatch between original and current simulations!")
}
```

>>>>

setup <- expand_grid(n_obs = n_obs,
                     truth = model_truth,
                     same = model_same,
                     differ = model_differ,
                     mod_load = c(3),
                     mod_int = c(3),
                     extract_fns = list(extract_fns),
                     group.equal = list(c("loadings", "intercepts")),
                     auto.fix.first = FALSE)
to_export <- ls_funs() %>% map(get)
to_export <- c(list(setup = setup), to_export)
RNGkind("L'Ecuyer-CMRG")
set.seed(params$seed)
res_raw %<-% 
  generate_data(n_sim,
                setup,
                furrr_options(
                  globals = to_export,
                  seed = params$seed,
                  packages = c("furrr", "lavaan", "tidyverse")
                ))
```

@@

```{r checksum}
# compute checksum using md5
checksum <- digest::digest(res_raw, "md5")
if(checksum != "e3b116b36c2a267d0e848e692b76fc1a"){
  warning("Mismatch between original and current simulations!")
}
```
